### 2019-03-10 papers/journal/conclusion.tex
Improvement in the Related work section and changed the TODO to the respective work

In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
Our model of VTSs is static graphs.
%
In future, we will study the dynamic behaviors of VTSs.
%
It will allow us to predict behaviors after the perturbations in the VTSs
and more ways to test the predicted synthesis results.

\todo{SA: Rough outline of the answers needed in the future work section}
1. why this tool was biologically helpful?
\begin{itemize}
	\item we do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries. 
	\item With this tool, we make multiple new easily testable predictions. So it is very likely to hasten discoveries in this field.
\end{itemize}

2.  What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
\\
\textbf{Encode Dynamic behaviour of the VTS:} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation. Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.
Maturation  is  evident  in  the  Golgi  apparatus  and  in  the  endocytic system. 
Including this behaviour of the compartments in the model would allow it to make more accurate predictions.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
Our model of VTSs is static graphs.
%
In future, we will study the dynamic behaviors of VTSs.
%
It will allow us to predict behaviors after the perturbations in the VTSs
and more ways to test the predicted synthesis results.\\

\ankit{A rough outline of the answers needed in the future work section}
\begin{enumerate}
  \item why this tool was biologically helpful?
        \begin{itemize}
        	\item we do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries. 
        	\item With this tool, we make multiple new easily testable predictions. So it is very likely to hasten discoveries in this field.
        \end{itemize}
  \item What  needs  to  be  done  to  use  these  tools  to  real  world  BIO problems. In what aspect you want more, where it lagged.
\end{enumerate}

\textbf{Encode Dynamic behaviour of the VTS:} A major aspect of the biological cell’s VTS that the current model is missing is compartment maturation. Compartments of the cell are not in steady state; rather they are changing in molecular composition due to imbalances in incoming and outgoing molecular flux on vesicles.
Maturation  is  evident  in  the  Golgi  apparatus  and  in  the  endocytic system. 
Including this behaviour of the compartments in the model would allow it to make more accurate predictions.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2019-03-10 papers/journal/intro.tex
Improvement in the Related work section and changed the TODO to the respective work

\todo{schematic of snare regulatory network}
In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
%
\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
\newline SM proteins have multiple modes of SNARE regulation: 
\begin{itemize}
	\item SM proteins can hold
	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
	complexes.
	%
	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
	form.
	%
	\item Finally, SM proteins bind the fully assembled
	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
	%
	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
\end{itemize}

\textbf{Major paths in the vesicle transport network}:
\todo{schematic of intracellular compartments and  major routes}
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.

@@

\subsection{Graph connectivity is an interesting and accessible property of the VTS}
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths. The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments. But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.

\todo{SA: Need more text on the importance and relevance of PROPRTY OF CONNECTIVITY}
One such benchmark is provided by our result about connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].

\todo{SA: We need not specify Synthesis here. Only connectivity use next subsection to build this. SM: but this is the para where we explain why connectivity is interesting an biological property}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.

>>>>

\somya{schematic of snare regulatory network}
In keeping with their central role in vesicle transport,both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
%
\newline Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
\newline SM proteins have multiple modes of SNARE regulation: 
\begin{itemize}
	\item SM proteins can hold
	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
	complexes.
	%
	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
	form.
	%
	\item Finally, SM proteins bind the fully assembled
	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
	%
	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
\end{itemize}

\somya{schematic of intracellular compartments and  major routes}
\textbf{Major paths in the vesicle transport network}:
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.

@@

\subsection{Graph connectivity is an interesting and accessible property of the VTS}
\ankit{This section requires serious work and best written by Mukund.}
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths. The molecules of the VTS, their interactions and modes of regulation have been worked out to a large extent through cell-biological experiments. But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks.

\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
One such benchmark is provided by our result about connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].

\ankit{We need not specify Synthesis here. Only connectivity use next subsection to build this.}
\somya{But this is the para where we explain why connectivity is interesting an biological property}
The vesicle transport graphs available today for eukaryotic organisms are incomplete themselves. 
%
In this situation, we use our result as a tool to predict missing edges which satisfy the graph connectivity constraint. 
%
These predictions are intended to be used as guides for future experiments. 
%
A mismatch between our predictions and experiments would indicate that our current understanding of the VTS molecules is necessarily incomplete. 
%
Note that, on the other hand, if our predictions are experimentally confirmed, it does not imply that our understanding of the VTS is complete.

### 2019-03-10 papers/journal/problem.tex
Fixed references and other latex LOG's, Fig and other issues continues
Improvement in the Related work section and changed the TODO to the respective work

 \todo{A dummy template} \textbf{QBF search problem:}
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$,and
$G$ is not $k$-connected.

>>>>

\ankit{This is a dummy template. need a rewrite.} \textbf{QBF search problem:}
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$,and
$G$ is not $k$-connected.

### 2019-03-10 papers/journal/related.tex
qbf mentioned in the related work section
Improvement in the Related work section and changed the TODO to the respective work

One of the prominent areas of application of SAT/SMT solvers is modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
%
The gene regulatory network question is encoded into a Boolean satisfiability problem and then SAT and SMT solvers are used to solve the generated formula. 
%
The~\cite{rosenblueth2014inference, batt2010efficient, dunn2014defining} use symbolic SAT solving approach whereas~\cite{giacobbe2015model, yordanov2016method} present an SMT based encoding of the problem.
% 
We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system. 
%
To our best knowledge this series of work is the first application
of formal methods to vesicle traffic networks.

>>>>

One of the prominent areas of application of SAT and SMT solvers is modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
%
The gene regulatory network question is encoded either directly as a Boolean satisfiability problem or in addition with the combinations of background theories.
%
The generated formula is then solved with the help of a SAT solver. 
%
The~\cite{rosenblueth2014inference} uses symbolic model checking approach on the qualitative
models of regulatory networks.
%
Whereas,~\cite{dunn2014defining}  uses symbolic, SAT-based approach on the Boolean network model. 
%
The~\cite{giacobbe2015model, yordanov2016method} presents an SMT based encoding of the problem based on the presented Boolean model.
%

We have extended the application of SAT and SMT solvers to a comparatively more complex biological transport network~\cite{mani2016stacking} namely vesicle traffic system (VTS). 
%
%Unlike the GNR, not many  VTS
We have presented both SAT and SMT based encoding for our Boolean model of the VTS.
%
We have also introduced the use of QBF solvers and it's encoding in this context.
% 
To our best knowledge our work is the first application
of formal methods to the vesicle traffic networks.
